A Generalized Sphere Theorem for Positively Curved Combinatorial 3-Manifolds

### 2013-04-14 paper/paper.tex
more writing

Differential geometry is of central importance not only to geometers but also topologists, physicists and, increasingly, many of those interested in applied topics such as finite element analysis and computer graphics. One new offshoot in this area is {\em discrete differential geometry} (DDG) which seeks discrete analogues to the classical theorems and concepts from differential geometry. Since many computational treatments of differential geometry involve discretizing shapes, this subject has particular relevance for those with applied interests \cite{grinspun2006discrete}. Other recent DDG work can be found in \cite{BMM,Crowley,EMM,forman2,GGL1,GGL2,GGL3,stone}.

@@

\noindent Note that this bound is sharp, since the real projective space $\mathbb{RP}^n$ admits a metric with uniform sectional curvature $K=1$ and diameter $\pi/2$. We should also note also that the diameter bound in Theorem \ref{thm:gove_shiohama} is exactly half the maximum diameter allowed by the Bonnet-Myers theorem:

@@

Probably the most natural discrete definition of distance in an abstract simplicial complexe is given in terms of edge paths.

>>>>

Differential geometry is of central importance not only to geometers but also topologists, physicists and, increasingly, many of those interested in applied topics such as finite element analysis and computer graphics. One new offshoot in this area is {\em discrete differential geometry} (DDG) which seeks discrete analogues to the classical theorems and concepts from differential geometry. Since many computational treatments of differential geometry involve discretizing shapes, this subject has particular relevance for those with applied interests, see \cite{grinspun2006discrete} for example. Other recent DDG work with a more pure-mathematics flavor can be found in \cite{BMM,Crowley,EMM,forman2,GGL1,GGL2,GGL3,stone}.

@@

\noindent Note that this bound is sharp, since the real projective space $\mathbb{RP}^n$ admits a metric with uniform sectional curvature $K=1$ and diameter $\pi/2$. We should also note also that the diameter bound in Theorem \ref{thm:grove_shiohama} is exactly half the maximum diameter allowed by the Bonnet-Myers theorem:

@@

Probably the most natural discrete definition of distance in an abstract simplicial complex is given in terms of edge paths.
